\textsf{Are large language models superhuman chemists?}

### 2024-10-25 src/tex/appendix.tex

\Cref{fig:performance_corpus_and_tiny} shows the performance of the models on the \chembench corpus and the \enquote{tiny} subset. The relative performance difference between both is actually quite similar across most models. This makes \enquote{tiny} subset a reliable subset for human baseline comparison and particularly valuable for rapid prototyping and initial model assessment phases.

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/corpus_human_comparison.pdf}
    \caption{\textbf{
        Performance of the models on the \chembench corpus and \enquote{tiny} subset.} The bar plot shows the fraction of questions that were answered completely correctly, highlighting the relative performance of different models on both \chembench corpus and the \enquote{tiny} subset.
        We see that the model ranking remains fairly consistent across both sets}  
    }
    \label{fig:performance_corpus_and_tiny}
    \script{corpus_humanset_performance.py}
\end{figure}

>>>>

\Cref{fig:performance_corpus_and_tiny} shows the performance of the models on the \chembench corpus and the \chembenchmini subset. The relative performance difference between both is actually quite similar across most models. This makes \chembenchmini subset a reliable subset for human baseline comparison and particularly valuable for rapid prototyping and initial model assessment phases.

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/corpus_human_comparison.pdf}
    \caption{\textbf{
        Performance of the models on the \chembench corpus and \chembenchmini subset.} The bar plot shows the fraction of questions that were answered completely correctly, highlighting the relative performance of different models on both \chembench corpus and the \chembenchmini subset.
        We see that the model ranking remains fairly consistent across both sets}  
    }
    \label{fig:performance_corpus_and_tiny}
    \script{corpus_humanset_performance.py}
\end{figure}
